---
title: "Trip ML Analysis Notebook"
output: html_notebook
---

Trip ML Analysis based on driving score data in mysql

plotHourOfDayTripCountData()
plotDayOfWeekTripCountData()
plotPeriodOfDayTripCountData()
plotTop20CityTripCountData()
plotWeatherTripCountData()
plotHourOfDayTripDurationData()

Common Function and Dataset
```{r}
source(here::here('dataset-mysql', 'MySQLDataSet.R'))

```


plotHourOfDayTripCountData

```{r}
plotHourOfDayTripCountData <- function()
{
  scoreData <- readScoreDataFiltered("select sHourofday, count(*) as tripcount from trips group by sHourofday order by sHourofday")
  #print(scoreData)
  
  library(ggplot2)
  library(ggmap)
  p <- 
    ggplot(data = data.frame(scoreData), aes(sHourofday,tripcount )) +
    geom_line(size = 1) +
    #title_with_subtitle(paste("Hourly Trip Count"), "Based on trip data") +
    expand_limits(y = 0) +
    #theme_tws(base_size = 12) +
    theme(legend.position = "bottom")
  return (p)
}
plotHourOfDayTripCountData();
```

plotDayOfWeekTripCountData

```{r}
plotDayOfWeekTripCountData <- function()
{
  scoreData <- readScoreDataFiltered("select sDayofweek, count(*) as tripcount from trips group by sDayofweek order by sDayofweek")
  #print(scoreData)
  
  library(ggplot2)
  library(ggmap)
  p <- 
    ggplot(data = data.frame(scoreData), aes(sDayofweek,tripcount )) +
    geom_line(size = 1) +
    #title_with_subtitle(paste("Daily Trip Count"), "Based on trip data") +
    expand_limits(y = 0) +
    #theme_tws(base_size = 12) +
    theme(legend.position = "bottom")
  #print(p)
  return (p)
}
plotDayOfWeekTripCountData()
```

plotPeriodOfDayTripCountData

```{r}
plotPeriodOfDayTripCountData <- function()
{
  scoreData <- readScoreDataFiltered("select dayperiod, count(*) as tripcount from trips group by dayperiod")
  #print(scoreData)
  
  library(ggplot2)
  library(ggmap)
  p <- 
    ggplot(data = data.frame(scoreData), aes(dayperiod,tripcount, group = 1 )) +
    geom_point() +
    geom_line(size = 1) +
    #title_with_subtitle(paste("Period of day Trip Count"), "Based on trip data") +
    expand_limits(y = 0) +
    #theme_tws(base_size = 12) +
    theme(legend.position = "bottom")
  #print(p)
  return (p)
}

plotPeriodOfDayTripCountData()
```

plotStartLocTripCountData

```{r}
plotStartLocTripCountData <- function()
{
  scoreData <- readScoreDataFiltered("select dayperiod, count(*) as tripcount from trips group by dayperiod")
  #print(scoreData)
  
  library(ggplot2)
  library(ggmap)
  p <- 
    ggplot(data = data.frame(scoreData), aes(dayperiod,tripcount, group = 1 )) +
    geom_point() +
    geom_line(size = 1) +
    #title_with_subtitle(paste("Period of day Trip Count"), "Based on trip data") +
    expand_limits(y = 0) +
    #theme_tws(base_size = 12) +
    theme(legend.position = "bottom")
  #print(p)
  return (p)
}
plotStartLocTripCountData();
```

plotTop20CityTripCountData

```{r}
plotTop20CityTripCountData <- function()
{
  scoreData <- readScoreDataFiltered("select count(*) as tripcount, g.city as city from trips t, geodata g where t.sLongitude = g.ilong
                                     and t.sLatitude = g.ilat
                                     group by city
                                     order by tripcount desc
                                     limit 20;")
  #print(scoreData)
  
  library(ggplot2)
  library(ggmap)
  p <- 
    ggplot(data = data.frame(scoreData), aes(city,tripcount, group = 1 )) +
    #geom_line(size = 1) +
    geom_bar(stat = "identity") +
    #title_with_subtitle(paste("Hourly Trip Count"), "Based on trip data") +
    expand_limits(y = 0) +
    #theme_tws(base_size = 12) +
    theme(legend.position = "bottom") + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
  #print(p)
  return (p)
}

plotTop20CityTripCountData()
```

plotWeatherTripCountData

```{r}
plotWeatherTripCountData <- function(conn)
{
  scoreData <- readScoreDataFiltered(conn, "select count(*) as tripcount, g.weather as weather from trips t, geodata g where t.sLongitude = g.ilong
                                     and t.sLatitude = g.ilat
                                     and weather is not null
                                     group by weather
                                     order by tripcount desc;")
  #print(scoreData)
  
  library(ggplot2)
  library(ggmap)
  p <- 
    ggplot(data = data.frame(scoreData), aes(weather,tripcount, group = 1 )) +
    #geom_line(size = 1) +
    geom_bar(stat = "identity") +
    #title_with_subtitle(paste("weather Trip Count"), "Based on trip data") +
    expand_limits(y = 0) +
    #theme_tws(base_size = 12) +
    theme(legend.position = "bottom") + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
  #print(p)
  return (p)
}

plotWeatherTripCountData()
```

plotHourOfDayTripDurationData

```{r}
plotHourOfDayTripDurationData <- function(conn)
{
  query <- "select ROUND(AVG(runtime)) as duration, sHourofday, count(*) as tripcount from trips 
            where overweekend = 'weekday' group by overweekend,sHourofday ORDER BY tripcount DESC
            ;"  
  scoreData <- readScoreDataFiltered(conn, query)

  library(ggplot2)
  library(ggmap)
  p <- 
    ggplot(data = data.frame(scoreData), aes(sHourofday, group = 1 )) + 
    geom_line(aes(y = duration, alpha = "  Median ") ) + 
    
    scale_y_continuous("trip duration in minutes\n") +
    #title_with_subtitle(paste("Hourly Trip Count"), "Based on trip data") +
    expand_limits(y = 0) +
    #theme_tws(base_size = 12) +
    theme(legend.position = "bottom") 
  #print(p)
  return (p)
}

plotHourOfDayTripDurationData()

```

plotCityPickupData

```{r}
plotCityPickupData <- function(conn, cityList, citylat, citylon,zoomlevel)
{
  query <- paste("select ilong, ilat from geodata where city in (", cityList,
              ");")  
  scoreData <- readScoreDataFiltered(conn, query)
  #print(scoreData)
  
  library(ggplot2)
  library(ggmap)
  
  mh_map = get_googlemap(center = c(citylon, citylat), zoom = zoomlevel, style = "feature:poi|visibility:off")
  p <- ggmap(mh_map, extent = "device") +
    geom_point(data=scoreData,
               aes(x = ilong, y=ilat),
               alpha = 0.0475,
               size = 4,
               shape=23, fill="blue",
               color = "#cc0000") +
    title_with_subtitle(cityList, "Pick ups") +
    theme_tws_map(base_size = 12)
  #print(p)
  return (p)
}

plotCityPickupData();
```

